`It Is Unbearable To Breathe Here': Air Quality, Open Incineration, And Misinformation In Blantyre, Malawi

### 2023-10-05 manuscript/manuscript-qech-air-quality-tilley.qmd
Show figure facet label in subscript

no_peaks_who

dat_in |> 
  mutate(peaks = case_when(
    indicator == "pm2.5" & value >  35 ~ TRUE,
    indicator == "pm10" & value >  70 ~ TRUE,
    TRUE ~ FALSE
  )) |> 
  mutate(date = as_date(date_time)) |> 
  group_by(indicator, location) |> 
  summarise(
    peaks = sum(peaks)
  ) |> 
  ungroup() |> 
  pivot_wider(names_from = indicator, values_from = peaks)

@@

@@

    TRUE ~ exposure_percent
  ))

@@

fig05 <- 
ggplot(data = percent_exposure,
       aes(fill = air_quality_who_annual, values = exposure_percent)) +
  geom_waffle(color ="white", size = 0.5, n_rows = 5, na.rm = TRUE) +
  coord_equal() +
  labs(fill = "WHO 2021 targets (annual)") +
  scale_fill_brewer(type = "div", palette = "RdYlBu", direction = -1) +
  scale_x_discrete(expand=c(0,0)) +
  scale_y_discrete(expand=c(0,0)) +
  facet_grid(location ~ indicator, switch = "y") +

@@

>>>>

no_peaks_who <- dat_in |> 
  mutate(peaks = case_when(
    indicator == "pm2.5" & value >  35 ~ TRUE,
    indicator == "pm10" & value >  70 ~ TRUE,
    TRUE ~ FALSE
  )) |> 
  mutate(date = as_date(date_time)) |> 
  group_by(indicator, location) |> 
  summarise(
    peaks = sum(peaks)
  ) |> 
  ungroup() |> 
  pivot_wider(names_from = indicator, values_from = peaks)

@@

# Create a custom labeller function
custom_labeller <- function(labels) {
  lapply(labels, function(x) bquote(.(x)))
}

@@

    TRUE ~ exposure_percent
  )) |> 
  mutate(indicator = case_when(
    indicator == "pm10" ~ "PM[10]",
    indicator == "pm2.5" ~ "PM[2.5]"
  )) |> 
  ungroup()

@@

fig05 <- ggplot(data = percent_exposure,
       aes(fill = air_quality_who_annual, values = exposure_percent)) +
  geom_waffle(color ="white", size = 0.5, n_rows = 5, na.rm = TRUE) +
  coord_equal() +
  labs(fill = "WHO 2021 targets (annual)") +
  scale_fill_brewer(type = "div", palette = "RdYlBu", direction = -1) +
  scale_x_discrete(expand=c(0,0)) +
  scale_y_discrete(expand=c(0,0)) +
  facet_grid(location~indicator, switch = "y", 
             labeller = labeller(location = custom_labeller, indicator = label_parsed)) +

@@

```{r}
# Load required libraries
library(ggplot2)

# Create example data
df <- data.frame(
  x = rep(1:3, each = 10),
  y = rnorm(30),
  group = rep(c("A[1]", "B[2]", "C[3]"), each = 10),
  category = rep(c("Cat 1", "Cat 2"), 15)
)

# Create a custom labeller function
custom_labeller <- function(labels) {
  lapply(labels, function(x) bquote(.(x)))
}

# Create a ggplot with subscript labels in facets
p <- ggplot(df, aes(x, y)) +
  geom_point() +
  facet_grid(category ~ group, labeller = labeller(category = custom_labeller, group = label_parsed))

# Print the plot
print(p)

### 2023-10-05 manuscript/manuscript-qech-air-quality-tilley.tex
Show figure facet label in subscript

\usepackage{booktabs}
\usepackage{caption}
\usepackage{longtable}
\usepackage{lineno}\linenumbers
\makeatletter
\makeatother
\makeatletter
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\AtBeginDocument{%
\ifdefined\contentsname
  \renewcommand*\contentsname{Table of contents}
\else
  \newcommand\contentsname{Table of contents}
\fi
\ifdefined\listfigurename
  \renewcommand*\listfigurename{List of Figures}
\else
  \newcommand\listfigurename{List of Figures}
\fi
\ifdefined\listtablename
  \renewcommand*\listtablename{List of Tables}
\else
  \newcommand\listtablename{List of Tables}
\fi
\ifdefined\figurename
  \renewcommand*\figurename{Figure}
\else
  \newcommand\figurename{Figure}
\fi
\ifdefined\tablename
  \renewcommand*\tablename{Table}
\else
  \newcommand\tablename{Table}
\fi
}
\@ifpackageloaded{float}{}{\usepackage{float}}
\floatstyle{ruled}
\@ifundefined{c@chapter}{\newfloat{codelisting}{h}{lop}}{\newfloat{codelisting}{h}{lop}[chapter]}
\floatname{codelisting}{Listing}
\newcommand*\listoflistings{\listof{codelisting}{List of Listings}}
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\@ifpackageloaded{subcaption}{}{\usepackage{subcaption}}
\makeatother
\makeatletter
\@ifpackageloaded{tcolorbox}{}{\usepackage[skins,breakable]{tcolorbox}}
\makeatother
\makeatletter
\@ifundefined{shadecolor}{\definecolor{shadecolor}{rgb}{.97, .97, .97}}
\makeatother
\makeatletter
\makeatother
\makeatletter
\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[breakable, sharp corners, frame hidden, interior hidden, enhanced, borderline west={3pt}{0pt}{shadecolor}, boxrule=0pt]}{\end{tcolorbox}}\fi
\makeatother
\makeatletter
\makeatother
\journal{Environment International}
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\usepackage[]{natbib}
\bibliographystyle{elsarticle-harv}
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same} % disable monospaced font for URLs
\hypersetup{
  pdftitle={`It Is Unbearable To Breathe Here': Air Quality, Open Incineration, And Misinformation In Blantyre, Malawi},
  pdfauthor={Elizabeth Tilley; Hope Chilunga; Jonathan Kwangulero; Lars Schöbitz; Saloni Vijay; Heiko Heilgendorff; Marc Kalina},
  pdfkeywords={waste management, healthcare waste, trash burning, air
quality, Malawi, urbanisation},
  colorlinks=true,
  linkcolor={blue},
  filecolor={Maroon},
  citecolor={Blue},
  urlcolor={Blue},
  pdfcreator={LaTeX via pandoc}}

@@

\hypertarget{tbl-peaks}{}
\begin{longtable}[]{@{}lrrr@{}}
\caption{\label{tbl-peaks}Peaks for both PM\textsubscript{2.5} and
PM\textsubscript{10} are the number of data points above the WHO interim
target 1 (annual) which is the least stringent; the number of
observations recorded (count) is provided for reference.}\tabularnewline
\toprule\noalign{}
location & n & pm10 & pm2.5 \\
\midrule\noalign{}
\endfirsthead
\toprule\noalign{}
location & n & pm10 & pm2.5 \\
\midrule\noalign{}
\endhead
\bottomrule\noalign{}
\endlastfoot
Administration & 10900 & 171 & 0 \\
Guardian Shelter & 11032 & 4529 & 0 \\
Lighthouse Clinic & 11472 & 4365 & 0 \\
Lions Sight & 11749 & 91 & 0 \\
Malaria & 12031 & 617 & 0 \\
Mercy James & 12193 & 736 & 0 \\
Ward 6B & 11861 & 1113 & 0 \\
uMoyo & 10637 & 703 & 0 \\
\end{longtable}

@@

>>>>

\usepackage{booktabs}
\usepackage{caption}
\usepackage{longtable}
\usepackage{lineno}\linenumbers
\makeatletter
\makeatother
\makeatletter
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\AtBeginDocument{%
\ifdefined\contentsname
  \renewcommand*\contentsname{Table of contents}
\else
  \newcommand\contentsname{Table of contents}
\fi
\ifdefined\listfigurename
  \renewcommand*\listfigurename{List of Figures}
\else
  \newcommand\listfigurename{List of Figures}
\fi
\ifdefined\listtablename
  \renewcommand*\listtablename{List of Tables}
\else
  \newcommand\listtablename{List of Tables}
\fi
\ifdefined\figurename
  \renewcommand*\figurename{Figure}
\else
  \newcommand\figurename{Figure}
\fi
\ifdefined\tablename
  \renewcommand*\tablename{Table}
\else
  \newcommand\tablename{Table}
\fi
}
\@ifpackageloaded{float}{}{\usepackage{float}}
\floatstyle{ruled}
\@ifundefined{c@chapter}{\newfloat{codelisting}{h}{lop}}{\newfloat{codelisting}{h}{lop}[chapter]}
\floatname{codelisting}{Listing}
\newcommand*\listoflistings{\listof{codelisting}{List of Listings}}
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\@ifpackageloaded{subcaption}{}{\usepackage{subcaption}}
\makeatother
\makeatletter
\@ifpackageloaded{tcolorbox}{}{\usepackage[skins,breakable]{tcolorbox}}
\makeatother
\makeatletter
\@ifundefined{shadecolor}{\definecolor{shadecolor}{rgb}{.97, .97, .97}}
\makeatother
\makeatletter
\makeatother
\makeatletter
\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[borderline west={3pt}{0pt}{shadecolor}, boxrule=0pt, interior hidden, enhanced, frame hidden, breakable, sharp corners]}{\end{tcolorbox}}\fi
\makeatother
\makeatletter
\makeatother
\journal{Environment International}
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\usepackage[]{natbib}
\bibliographystyle{elsarticle-harv}
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same} % disable monospaced font for URLs
\hypersetup{
  pdftitle={`It Is Unbearable To Breathe Here': Air Quality, Open Incineration, And Misinformation In Blantyre, Malawi},
  pdfauthor={Elizabeth Tilley; Hope Chilunga; Jonathan Kwangulero; Lars Schöbitz; Saloni Vijay; Heiko Heilgendorff; Marc Kalina},
  pdfkeywords={waste management, healthcare waste, trash burning, air
quality, Malawi, urbanisation},
  colorlinks=true,
  linkcolor={blue},
  filecolor={Maroon},
  citecolor={Blue},
  urlcolor={Blue},
  pdfcreator={LaTeX via pandoc}}

@@

\hypertarget{tbl-peaks}{}
\begin{longtable}[]{@{}lrrr@{}}
\caption{\label{tbl-peaks}Peaks for both PM\textsubscript{2.5} and
PM\textsubscript{10} are the number of data points above the WHO interim
target 1 (annual) which is the least stringent; the number of
observations recorded (count) is provided for reference.}\tabularnewline
\toprule\noalign{}
location & n & pm10 & pm2.5 \\
\midrule\noalign{}
\endfirsthead
\toprule\noalign{}
location & n & pm10 & pm2.5 \\
\midrule\noalign{}
\endhead
\bottomrule\noalign{}
\endlastfoot
Administration & 10900 & 171 & 94 \\
Guardian Shelter & 11032 & 4529 & 5314 \\
Lighthouse Clinic & 11472 & 4365 & 3891 \\
Lions Sight & 11749 & 91 & 14 \\
Malaria & 12031 & 617 & 578 \\
Mercy James & 12193 & 736 & 749 \\
Ward 6B & 11861 & 1113 & 1236 \\
uMoyo & 10637 & 703 & 399 \\
\end{longtable}

@@

\includegraphics{manuscript-qech-air-quality-tilley_files/figure-pdf/unnamed-chunk-9-1.pdf}
